\subsection{Monster Lair}

\begin{multicols}{2}
		
		\textbf{1. Hoard}\\
		
		\tabpar[1]{Treasure! You might find some neat stuff inside if its not enchanted.}
		\tabpar[1]{\textbf{TN:} MAG 3 + [TIER] \cirpip}\skipline
		
		\textbf{2. Fresh Tracks}\\
		
		\tabpar[1]{Follow the tracks if you are fast enough to catch who made them.}
		\tabpar[1]{\textbf{TN:} SPD 4 + [TIER] \cirpip}\skipline
		
		\textbf{3. Pile of Bones}\\
		
		\tabpar[1]{Search the bones for remaining valuables if you can stomach it.}
		\tabpar[1]{\textbf{TN:} DEF 4 + [TIER] \cirpip}\skipline
		
		\textbf{4. Lost Hound}\\
		
		\tabpar[1]{A lost hunting dog. You think its owner came monster hunting.}
		\tabpar[1]{\textbf{TN:} SPD 4 + [TIER] \cirpip}\skipline
		
		\textbf{5. Giant Rat}\\
		
		\tabpar[1]{He makes all of the rules.}
		\tabpar[1]{\textbf{TN:} ATK 5 + [TIER] \tripip}\skipline
		
		\textbf{6. Ambush}\\
		
		\tabpar[1]{Ambushed by an unknown foe, fight back the best you can.}
		\tabpar[1]{\textbf{TN:} ATK 6 + [TIER] \tripip}\skipline
		
		\columnbreak
		
		\textbf{7. Bear Trap}\\
		
		\tabpar[1]{Many bear traps lie between you and your destination.}
		\tabpar[1]{\textbf{TN:} SPD 5 + [TIER] \cirpip}\skipline
		
		\textbf{8. Signs}\\
		
		\tabpar[1]{Marked with warnings, interpret them to learn what’s ahead.}
		\tabpar[1]{\textbf{TN:} MAG 5 + [TIER] \cirpip}\skipline
		
		\textbf{9. Cave-in}\\
		
		\tabpar[1]{The lair’s ceiling is caving in. Get out before you’re crushed.}
		\tabpar[1]{\textbf{TN:} SPD 5 + [TIER] \cirpip}\skipline
		
		\textbf{10. Knightslayer Snail}\\
		
		\tabpar[1]{The mortal enemy of Knights and Squires: the snail.}
		\tabpar[1]{\textbf{TN:} DEF 5 + [TIER] \tripip}\skipline
		
		\textbf{11. Summoning Circle}\\
		
		\tabpar[1]{An incomplete summoning circle. You may be able to finish the ritual...}
		\tabpar[1]{\textbf{TN:} MAG 6 + [TIER] \cirpip}\skipline
		
		\textbf{12. Monster Hunter}\\
		
		\tabpar[1]{A hunter missing its hound. Have you seen it?}
		\tabpar[1]{\textbf{TN:} CHA 7 + [TIER] \cirpip}\skipline
		
		\columnbreak
		
		\textbf{13. Harpies}\\
		
		\tabpar[1]{They made a nest here, and you seem like easy prey.}
		\tabpar[1]{\textbf{TN:} ATK 6 + [TIER] \tripip}\skipline
		
		\textbf{14. Stalking Beast}\\
		
		\tabpar[1]{An unknown monster is looking for you, and you can’t fight it. Hide!}
		\tabpar[1]{\textbf{TN:} SPD 6 + [TIER] \tripip}\skipline
		
		\textbf{15. Cockatrice}\\
		
		\tabpar[1]{Be mindful of its petrifying gaze. You must counter its magic.}
		\tabpar[1]{\textbf{TN:} MAG 6 + [TIER] \tripip}\skipline
		
		\columnbreak
		
		\textbf{16. Corpse Pit}\\
		
		\tabpar[1]{Remains of meals from the boss, but you see the glint of gold...}
		\tabpar[1]{\textbf{TN:} DEF 6 + [TIER] \cirpip}\skipline
		
		\textbf{17. Loot Pile}\\
		
		\tabpar[1]{A glinting pile of gold. Try to take some, but be quick.}
		\tabpar[1]{\textbf{TN:} SPD 7 + [TIER] \cirpip}\skipline
		
		\textbf{18. Ogre}\\
		
		\tabpar[1]{A great man armed with a heavy club and an insatiable hunger.}
		\tabpar[1]{\textbf{TN:} ATK 8 + [TIER] \cirpip}\skipline
\end{multicols}
\textbf{BOSS: Rabbit} -- An unassuming but lethal beast that cannot be slayed by you or any.\\
\textbf{TN:} DEF 11 \tripip \& SPD 12 \cirpip