\subsection{Ruins}

\begin{multicols}{2}
		
		\textbf{1. Old Cellar}\\
		
		\tabpar[1]{May contain treasures left behind, or rotting food.}
		\tabpar[1]{\textbf{TN:} DEF 3 + [TIER] \cirpip}\skipline
		
		\textbf{2. Hermit}\\
		
		\tabpar[1]{He’s lived alone for decades. Who knows what secrets he holds...}
		\tabpar[1]{\textbf{TN:} CHA 3 + [TIER] \cirpip}\skipline
		
		\textbf{3. Pack of Stray Dogs}\\
		
		\tabpar[1]{Left behind by their owners, now you’re in their territory.}
		\tabpar[1]{\textbf{TN:} SPD 4 + [TIER] \tripip}\skipline
		
		\textbf{4. Crumbling Room}\\
		
		\tabpar[1]{An old bedroom that falls apart when you enter.}
		\tabpar[1]{\textbf{TN:} SPD 4 + [TIER] \cirpip}\skipline
		
		\textbf{5. Bookshelf}\\
		
		\tabpar[1]{You can’t tell if it contains old grimoires or romance novels.}
		\tabpar[1]{\textbf{TN:} MAG 5 + [TIER] \cirpip}\skipline
		
		\textbf{6. Bandit}\\
		
		\tabpar[1]{A bandit looking to score some cash. You have some cash.}
		\tabpar[1]{\textbf{TN:} ATK 6 + [TIER] \tripip}\skipline
		
		\columnbreak
		
		\textbf{7. Tainted Well}\\
		
		\tabpar[1]{It sickens you when you take a sip. Resist the blight.}
		\tabpar[1]{\textbf{TN:} DEF 5 + [TIER] \cirpip}\skipline
		
		\textbf{8. Broken Windmill}\\
		
		\tabpar[1]{Someone must have confused it for a giant.}
		\tabpar[1]{\textbf{TN:} MAG 5 + [TIER] \cirpip}\skipline
		
		\textbf{9. Mimic}\\
		
		\tabpar[1]{Roll 1d6. If you have an equivalent die, steal its treasure.}\skipline
		
		\textbf{10. Dead Horse}\\
		
		\tabpar[1]{Maybe if you beat it enough, something interesting will happen.}
		\tabpar[1]{\textbf{TN:} ATK 5 + [TIER] \cirpip}\skipline
		
		\textbf{11. Hidden Room}\\
		
		\tabpar[1]{Equal chance of accessing it as there is of activating a trap.}
		\tabpar[1]{\textbf{TN:} SPD 6 + [TIER] \cirpip}\skipline
		
		\textbf{12. Bridge Troll}\\
		
		\tabpar[1]{Trying to extort you. Luckily, all he wants is coin.}
		\tabpar[1]{\textbf{TN:} ATK 7 + [TIER] \tripip}\skipline
		
		\columnbreak
		
		\textbf{13. Doppelganger}\\
		
		\tabpar[1]{One among you has been replaced with a doppelganger. Find it!}
		\tabpar[1]{\textbf{TN:} MAG 6 + [TIER] \tripip}\skipline
		
		\textbf{14. Zombies}\\
		
		\tabpar[1]{Living dead remains of the old villagers who didn’t leave.}
		\tabpar[1]{\textbf{TN:} ATK 6 + [TIER] \tripip}\skipline
		
		\textbf{15. Broken Wagon}\\
		
		\tabpar[1]{Someone must have beaten its horses.}
		\tabpar[1]{\textbf{TN:} DEF 6 + [TIER] \tripip}\skipline
		
		\columnbreak
		
		\textbf{16. Booby Trap}\\
		
		\tabpar[1]{Seems pretty hard to miss in hindsight, but you fell on it.}
		\tabpar[1]{\textbf{TN:} SPD 6 + [TIER] \cirpip}\skipline
		
		\textbf{17. Plague Pit}\\
		
		\tabpar[1]{The resting place of the ruin’s original inhabitants.}
		\tabpar[1]{\textbf{TN:} DEF 7 + [TIER] \cirpip}\skipline
		
		\textbf{18. Derelict Church}\\
		
		\tabpar[1]{An abandoned church. Something feels... wrong.}
		\tabpar[1]{\textbf{TN:} MAG 8 + [TIER] \tripip}
	
\end{multicols}

\textbf{BOSS: Ancient Robot} -- A machine made by the original villagers. Try to deactivate it.\\
\textbf{TN:} MAG 11 \cirpip\& DEF 12 \tripip