\subsection{Defeat the Demon Lord}

\begin{multicols}{2}
	\begin{tabbox}[2][2]
		
		\textbf{3. Imp}\\
		
		\tabpar[1]{A small and weak demon. It might let you pass if you scare it.}
		\tabpar[1]{\textbf{TN:} CHA 11 \cirpip}\skipline
		
		\textbf{4. Trophy Room}\\
		
		\tabpar[1]{Filled with horrifying trophies and conquests of the Demon Lord.}
		\tabpar[1]{\textbf{TN:} DEF 11 \cirpip}\skipline
		
		\textbf{5. Trapped Hall}\\
		
		\tabpar[1]{You are stuck in a corridor with dozens upon dozens of traps.}
		\tabpar[1]{\textbf{TN:} SPD 12 \cirpip}\skipline
		
		\textbf{6. Cultists}\\
		
		\tabpar[1]{They believe they will be spared if they worship the Demon Lord.}
		\tabpar[1]{\textbf{TN:} MAG 12] \tripip}\skipline
		
		\textbf{7. Miasma}\\
		
		\tabpar[1]{The mist of sickness and death inundates the halls of the castle.}
		\tabpar[1]{\textbf{TN:} DEF 13 \cirpip}\skipline
		
		\textbf{8. Prisoners}\\
		
		\tabpar[1]{Set them free, but assure that you will keep them safe.}
		\tabpar[1]{\textbf{TN:} CHA 11 \cirpip}\skipline
		
		\textbf{9. Devil Butler}\\
		
		\tabpar[1]{A servant of the Demon Lord who will die protecting his master.}
		\tabpar[1]{\textbf{TN:} ATK 12 \tripip}\skipline
		
		\textbf{10. Hellfire}\\
		
		\tabpar[1]{Unholy flames surround you, trying to scorch your flesh and soul.}
		\tabpar[1]{\textbf{TN:} DEF 13 \cirpip}\
		
		\columnbreak
		
		\textbf{11. Hallway of Living? Armor}\\
		
		\tabpar[1]{A long hallway lined with suits of armor. Did that one move?}
		\tabpar[1]{\textbf{TN:} SPD 12 \tripip}\skipline
		
		\textbf{12. Basilisk}\\
		
		\tabpar[1]{Beware its petrifying breath.}
		\tabpar[1]{\textbf{TN:} DEF 14 \tripip}\skipline
		
		\textbf{13. Alchemy Lab}\\
		
		\tabpar[1]{Reagents and materials fill the cabinets. Some may be helpful...}
		\tabpar[1]{\textbf{TN:} MAG 12 \cirpip}\skipline
		
		\textbf{14. Chimera}\\
		
		\tabpar[1]{An artificial amalgamation of creatures, full of agony and wrath.}
		\tabpar[1]{\textbf{TN:} ATK 13 \tripip}\skipline
		
		\textbf{15. Lost Knight}\\
		
		\tabpar[1]{Crestfallen and unwilling to proceed, he may be able to assist.}
		\tabpar[1]{\textbf{TN:} CHA 11 \cirpip}\skipline
		
		\textbf{16. Grand Library}\\
		
		\tabpar[1]{Filled with ancient and lost knowledge. Don’t delve too deep.}
		\tabpar[1]{\textbf{TN:}MAG 12 \cirpip}\skipline
		
		\textbf{17. Demon Warrior}\\
		
		\tabpar[1]{A soldier from hell and a slayer of countless men.}
		\tabpar[1]{\textbf{TN:} ATK 14 \tripip}\skipline
		
		\textbf{18. Endless Stairs}\\
		
		\tabpar[1]{Rumors say if you jump back quickly enough, you will be able to escape.}
		\tabpar[1]{\textbf{TN:} SPD 13 \cirpip}
		
	\end{tabbox}
\end{multicols}

\textbf{BOSS: DEMON LORD} -- Defeat the Demon Lord and banish him -- or the world will be his.\\
\textbf{TN:} ATK 20 \tripip \& MAG 20 \cirpip