\subsection{Abandoned? Mine}

\begin{multicols}{2}
\begin{tabbox}[2][2]
	
	\textbf{1. Drunk Miners}\\
	
	\tabpar[1]{They won’t let you pass unless you can out-drink them.}
	\tabpar[1]{\textbf{TN:} DEF 3 + [TIER] \cirpip}\skipline
	
	\textbf{2. Lost Miner}\\
	
	\tabpar[1]{Convince him you mean no harm, and guide him to safety.}
	\tabpar[1]{\textbf{TN:} CHA 3 + [TIER] \cirpip}\skipline
	
	\textbf{3. Tunnel Collapse}\\
	
	\tabpar[1]{Run away before you are crushed like my hopes and dreams.}
	\tabpar[1]{\textbf{TN:} SPD 4 + [TIER] \cirpip}\skipline
	
	\textbf{4. Toxic Gases}\\
	
	\tabpar[1]{You should’ve brought a canary... and shouldn't have dressed in yellow.}
	\tabpar[1]{\textbf{TN:} DEF 4 + [TIER] \cirpip}\skipline
	
	\textbf{5. Flooded Shaft}\\
	
	\tabpar[1]{Hold your breath and look for goodies in the depths.}
	\tabpar[1]{\textbf{TN:} SPD 5 + [TIER] \cirpip}\skipline
	
	\textbf{6. Cave Troll}\\
	
	\tabpar[1]{Came down here to hide from the sunlight and got lost.}
	\tabpar[1]{\textbf{TN:} ATK 6 + [TIER] \tripip}\skipline

	\textbf{7. Kobolds}\\

	\tabpar[1]{A hunting party looking for food to eat, and you look really tasty.}
	\tabpar[1]{\textbf{TN:} ATK 5 + [TIER] \tripip}\skipline
	
	\textbf{8. Cave Paintings}\\
	
	\tabpar[1]{Either drawings of animals, or long forgotten magics.}
	\tabpar[1]{\textbf{TN:} MAG 5 + [TIER] \cirpip}\skipline
	
	\textbf{9. Cave Shrooms}\\
	
	\tabpar[1]{Definitely \so{(Not)} safe to eat \so{? (!)}}
	\tabpar[1]{\textbf{TN:} DEF 5 + [TIER] \cirpip}\skipline
	
	\columnbreak
	
	\textbf{10. Glowing Rocks}\\
	
	\tabpar[1]{Valuable magical rocks, do not touch with bare hands.}
	\tabpar[1]{\textbf{TN:} MAG 5 + [TIER] \cirpip}\skipline
	
	\textbf{11. Ore Vein}\\
	
	\tabpar[1]{It will take a lot of work to get it out without proper equipment.}
	\tabpar[1]{\textbf{TN:} ATK 6 + [TIER] \cirpip}\skipline
	
	\textbf{12. Underground Village}\\
	
	\tabpar[1]{Lost to time, you can trade light for iron and stone.}
	\tabpar[1]{\textbf{TN:} CHA 7 + [TIER] \cirpip}\skipline
	
	\textbf{13. Bat Swarm}\\
	
	\tabpar[1]{Run away or you’ll drown in bats!}
	\tabpar[1]{\textbf{TN:} SPD 7 + [TIER] \tripip}\skipline
	
	\textbf{14. Tight Tunnel}\\
	
	\tabpar[1]{Very claustrophobic, no one would willingly enter there. Unless...}
	\tabpar[1]{\textbf{TN:} SPD 6 + [TIER] \cirpip}\skipline
	
	\textbf{15. Underground River}\\
	
	\tabpar[1]{Bottomless and eerily cold waters, just hope it’s not the Styx.}
	\tabpar[1]{\textbf{TN:} DEF 6 + [TIER] \cirpip}\skipline
	
	\textbf{16. Giant Bat}\\
	
	\tabpar[1]{A creature of the night, its echolocation can kill.}
	\tabpar[1]{\textbf{TN:} ATK 6 + [TIER] \tripip}\skipline
	
	\textbf{17. Earthquake}\\
	
	\tabpar[1]{The earth rumbles in anger at your intrusion to the underground world.}
	\tabpar[1]{\textbf{TN:} DEF 7 + [TIER] \cirpip}\skipline
	
	\textbf{18. Lava Flow}\\
	
	\tabpar[1]{The veins of the earth open before you, and spew molten blood.}
	\tabpar[1]{\textbf{TN:} SPD 8 + [TIER] \cirpip}\skipline

\end{tabbox}

\end{multicols}

\textbf{BOSS: Dragon} -- Strong, smart, and prone to vanity, praise and a hidden blade will do the job.\\
\textbf{TN:} CHA 11 \tripip \& ATK 12 \tripip