\subsection{Crypt}

\begin{multicols}{2}
	\begin{tabbox}[2][2]
		
		\textbf{1. Undertaker}\\
		
		\tabpar[1]{A lone undertaker who hasn't realized the crypt is overrun.}
		\tabpar[1]{\textbf{TN:} CHA 3 + [TIER] \cirpip}\skipline
		
		\textbf{2. Illusory Wall}\\
		
		\tabpar[1]{You sense an illusory wall, try to find it without activating it.}
		\tabpar[1]{\textbf{TN:} MAG 3 + [TIER] \cirpip}\skipline
		
		\textbf{3. Arrow Trap}\\
		
		\tabpar[1]{You stepped on a pressure plate, disarm the trap or be skewered.}
		\tabpar[1]{\textbf{TN:} SPD 4 + [TIER] \cirpip}\skipline
		
		\textbf{4. Skeleton}\\
		
		\tabpar[1]{It rises from its tomb and starts rattling at you.}
		\tabpar[1]{\textbf{TN:} ATK 4 + [TIER] \tripip}\skipline
		
		\textbf{5. Cobwebs}\\
		
		\tabpar[1]{You’re trapped in a hallway filled with cobwebs from top to bottom.}
		\tabpar[1]{\textbf{TN:} DEF 5 + [TIER] \cirpip}\skipline
		
		\textbf{6. Ghost}\\
		
		\tabpar[1]{If you remind a ghost that it is already dead, it will pass away.}
		\tabpar[1]{\textbf{TN:} CHA 6 + [TIER] \cirpip}\skipline
		
		\textbf{7. Slime}\\
		
		\tabpar[1]{You touch something wet, sticky, and trying to digest you.}
		\tabpar[1]{\textbf{TN:} DEF 5 + [TIER] \tripip}\skipline
		
		\textbf{8. Stone Coffin}\\
		
		\tabpar[1]{Is treasure worth unearthing what should remain buried?}
		\tabpar[1]{\textbf{TN:} MAG 5 + [TIER] \cirpip}\skipline
		
		\textbf{9. Gargoyle}\\
		
		\tabpar[1]{Meant to guard from evil spirits. You look like evil spirits.}
		\tabpar[1]{\textbf{TN:} ATK 5 + [TIER] \tripip}\skipline
		
		\columnbreak
		
		\textbf{10. Mimic}\\
		
		\tabpar[1]{Roll 1d6. If you have an equivalent die, steal its treasure.}
        \skipline
		
		\textbf{11. Banshee}\\
		
		\tabpar[1]{A spirit of bad omens. Run away before you find out who dies.}
		\tabpar[1]{\textbf{TN:} SPD 6 + [TIER] \tripip}\skipline
		
		\textbf{12. Mysterious Altar}\\
		
		\tabpar[1]{A place of dark rituals? Or a long forgotten worship site?}
		\tabpar[1]{\textbf{TN:} MAG 7 + [TIER] \cirpip}\skipline
		
		\textbf{13. Snake Pit}\\
		
		\tabpar[1]{Snakes, why did it have to be snakes?}
		\tabpar[1]{\textbf{TN:} DEF 6 + [TIER] \cirpip}\skipline
		
		\textbf{14. "Bottomless" Pit}\\
		
		\tabpar[1]{You can see the bottom.}
		\tabpar[1]{\textbf{TN:} SPD 6 + [TIER] \cirpip}\skipline
		
		\textbf{15. Descending Ceiling}\\
		
		\tabpar[1]{Hold the ceiling up until someone can deactivate the trap.}
		\tabpar[1]{\textbf{TN:} DEF 6 + [TIER] \cirpip}\skipline
		
		\textbf{16. Ghoul}\\
		
		\tabpar[1]{A man-eating undead.}
		\tabpar[1]{\textbf{TN:} ATK 6 + [TIER] \tripip}\skipline
		
		\textbf{17. Talking Statue}\\
		
		\tabpar[1]{If you solve the riddle it recites, you might find treasure.}
		\tabpar[1]{\textbf{TN:} CHA 7 + [TIER] \cirpip}\skipline
		
		\textbf{18. Rolling Ball Trap}\\
		
		\tabpar[1]{You should have known that treasure was too good to be true.}
		\tabpar[1]{\textbf{TN:} SPD 8 + [TIER] \cirpip}\skipline
		
	\end{tabbox}
	
\end{multicols}

\textbf{BOSS: Necromancer} -- Has taken over the crypt, and will only leave if bested by wits.\\
\textbf{TN:} MAG 11 \tripip \& CHA 12 \tripip