\subsection{Haunted Forest}

\begin{multicols}{2}
	\begin{tabbox}[2][2]
		
		\textbf{1. Forest Clearing}\\
		
		\tabpar[1]{\textbf{A mysterious clearing that gives you goosebumps.}}
		\tabpar[1]{\textbf{TN:} MAG 3 + [TIER] \cirpip}\skipline
		
		\textbf{2. Snare Trap}\\
		
		\tabpar[1]{Left behind by poachers. Not dangerous unless it’s to your ego.}
		\tabpar[1]{\textbf{TN:} SPD 3 + [TIER] \cirpip}\skipline
		
		\textbf{3. Man-Eater Plant}\\
		
		\tabpar[1]{True to its name.}
		\tabpar[1]{\textbf{TN:} ATK 4 + [TIER] \tripip}\skipline
		
		\textbf{4. Swinging Log}\\
		
		\tabpar[1]{Another poacher’s trap. This one will be a headache.}
		\tabpar[1]{\textbf{TN:} SPD 4 + [TIER] \cirpip}\skipline
		
		\textbf{5. Wolf Pack}\\
		
		\tabpar[1]{The evil forces in this wood have brought this wolf pack to hunt you.}
		\tabpar[1]{\textbf{TN:} ATK 5 + [TIER] \cirpip}\skipline
		
		\textbf{6. Laurel Hell}\\
		
		\tabpar[1]{If you get in, you can’t get out.}
		\tabpar[1]{\textbf{TN:} DEF 6 + [TIER] \tripip}\skipline
		
		\textbf{7. Treant}\\
		
		\tabpar[1]{A living, talking tree who can be reasoned with.}
		\tabpar[1]{\textbf{TN:} CHA 5 + [TIER] \cirpip}\skipline
		
		\textbf{8. Pitcher Plant}\\
		
		\tabpar[1]{It swallows you whole. Resist the acid until you can escape.}
		\tabpar[1]{\textbf{TN:} MAG 5 + [TIER] \tripip}\skipline
		
		\textbf{9. Walking Shroom}\\
		
		\tabpar[1]{A common forest creature. Edible in a pinch, but questionable.}
		\tabpar[1]{\textbf{TN:} ATK 5 + [TIER] \tripip}\skipline
		
		\columnbreak
		
		\textbf{10. Old Druid}\\
		
		\tabpar[1]{Here to drive out the evil, but not yet convinced you’re here to help.}
		\tabpar[1]{\textbf{TN:} CHA 5 + [TIER] \cirpip}\skipline
		
		\textbf{11. The Silence}\\
		
		\tabpar[1]{All noise leaves the forest, a sign of danger beyond your abilities.}
		\tabpar[1]{\textbf{TN:} SPD 6 + [TIER] \tripip}\skipline
		
		\textbf{12. Aquelarre}\\
		
		\tabpar[1]{A witches’ reunion. Partake, and they will let you leave.}
		\tabpar[1]{\textbf{TN:} MAG 7 + [TIER] \cirpip}\skipline
		
		\textbf{13. Forest Spirit}\\
		
		\tabpar[1]{A lost forest spirit, looking for a source of life to sap.}
		\tabpar[1]{\textbf{TN:} DEF 6 + [TIER] \tripip}\skipline
		
		\textbf{14. Dryad}\\
		
		\tabpar[1]{Be prepared lest you be enthralled or turned into a plant.}
		\tabpar[1]{\textbf{TN:} MAG 6 + [TIER] \cirpip}\skipline
		
		\textbf{15. Poacher's Camp}\\
		
		\tabpar[1]{They’re hiding from someone, and will fight to keep hidden.}
		\tabpar[1]{\textbf{TN:} ATK 6 + [TIER] \tripip}\skipline
		
		\textbf{16. Elven Rangers}\\
		
		\tabpar[1]{They are looking for someone, and must be convinced it’s not you.}
		\tabpar[1]{\textbf{TN:} CHA 6 + [TIER] \cirpip}\skipline
		
		\textbf{17. Deep Fog}\\
		
		\tabpar[1]{You can’t see your hand held out before you. Stay on guard.}
		\tabpar[1]{\textbf{TN:} DEF 7 + [TIER] \tripip}\skipline
		
		\textbf{18. Fairy Ring}\\
		
		\tabpar[1]{You stepped into a fairy ring. Step away before you are taken.}
		\tabpar[1]{\textbf{TN:} SPD 8 + [TIER] \cirpip}\skipline
		
	\end{tabbox}
	
\end{multicols}

\textbf{BOSS: Cursed Tree} -- A host of hexes, fight it so you may prevent evil from spreading.\\
\textbf{TN:} ATK 11 \tripip \& MAG 12 \tripip