\chapter{Dungeons}

To calculate the total Resources you bring back to the castle, multiply the dungeon’s Base Resources by the number of events completed successfully. Remember to add the tier of your Stables to both Resources before multiplying by the amount of successful events.

\skipline

At Tiers 2 \& 3, roll \textbf{2d6} per companion to determine the event. At Tiers 4 \& 5, roll \textbf{3d6} per companion to determine the event.

\skipline

If you bring more than five companions, you also fight the Boss. This is automatic and happens after you have completed the rest of the dungeon’s events. To defeat bosses, companions must overcome both TNs listed.

\skipline


\begin{tabbox}[4][4]
	\subsubsection{Abandoned? Mine}
	\tabpar[3]{Though taken over by a beast of sulfur, the materials needed for your forge lie within.}
	\tabpar[3]{\textbf{Resources:} 5 Iron \& 3 Stone}
	
	\subsubsection{Crypt}
	\tabpar[3]{An old tomb, now overrun by undead and their master, but within many treasures await.}
	\tabpar[3]{\textbf{Resources:} 5 Gold \& 3 Iron}
	
	\subsubsection{Haunted Forest}
	\tabpar[3]{Cursed by an ancient evil, and yet still home to bandits.}
	\tabpar[3]{\textbf{Resources:} 5 Lumber \& 3 Leather}
	
	\subsubsection{Monster Lair}
	\tabpar[3]{The lair of a great white beast and home to many others. Holds the treasures of misfortune seekers.}
	\tabpar[3]{\textbf{Resources:} 5 Leather \& 3 Gold}
	
	\subsubsection{Ruins}
	\tabpar[3]{There are many abandoned towns near the castle. Old secrets hide here.}
	\tabpar[3]{\textbf{Resources:} 5 Stone \& 3 Lumber}

\end{tabbox}

\pagebreak

\input{sections/dungeon-mine.tex}

\pagebreak

\input{sections/dungeon-crypt.tex}

\pagebreak

\input{sections/dungeon-forest.tex}

\pagebreak

\input{sections/dungeon-lair.tex}

\pagebreak

\input{sections/dungeon-ruins.tex}

\pagebreak